High Resolution Spectroscopic Analysis of Orphan Stream Giants

### 2012-07-28 2012-oss/draft-oss.tex
alpha elements for OSS1

4040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
Fe I abundance: 6.24 +/- 0.16 (149 lines)
SOC: 0.02, 6.18, 0.13
REW SOC: 0.03, 6.39, 0.04
Lambda SOC: 0.81e-05, 5.78, 0.38

@@

ALPHA ELEMENTS Mg, Si, Ca, Ti
==============

>>>>

5040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
Fe I abundance: 6.24 +/- 0.16 (149 lines)
SOC: 0.02, 6.18, 0.13
REW SOC: 0.03, 6.39, 0.04
Lambda SOC: 0.81e-05, 5.78, 0.38

@@

ALPHA ELEMENTS Mg, Si, Ca, Ti <-> (12, 
==============

Mg I: 6.56 +/- 0.10 (4 lines), Solar 7.60 +/- 0.04
Inspected all four line profiles; they look perfect.
SOC: // // 4.51e-05, 6.29, 0.29
[Mg I/Fe] = 0.16 +/- 0.10

Si I: 6.57 +/- 0.23 (4 lines), Solar 7.51 +/- 0.03
Inspected all four line profiles; they all look great (one is 'reasonable')
SOC: 0.04, 6.36, 0.22 // 0.17, 7.37, 0.28 // 7.75e-05, 6.11, 0.23
[Si I/Fe] = 0.26 +/- 0.23

Ca I: 5.48 +/- 0.14 (14 lines), Solar 6.34 +/- 0.04
Inspected all lines; they all look good.
SOC: // // 1.44e-04, 4.60, 0.70
[Ca I/Fe] = 0.34 +/- 0.14

Ti I: 3.73 +/- 0.15 (21 lines) Solar 4.95 +/- 0.05
Inspected all lines; they all look good.
SOC: // 0.36, 5.49, 0.42 // 2.94e-05, 3.59, 0.08
[Ti I/Fe] = -0.02 +/- 0.15

Ti II: 3.91 +/- 0.10 (25 lines) Solar 4.95 +/- 0.05
SOC: -0.02, 3.91, -0.09 // 0.22, 4.93, 0.43 // -2.70e-05, 4.01, -0.10
[Ti II/Fe] = 0.16 +/- 0.10
